---
title: "Systematic literature review"
bibliography: references.bib
title-block-banner: true
subtitle: "Analysis of references"
author:
  - name: Olivier Caron
    email: olivier.caron@dauphine.psl.eu
    affiliations: 
      name: "Paris Dauphine - PSL"
      city: Paris
      state: France
  - name: Christophe Benavent
    email: christophe.benavent@dauphine.psl.eu
    affiliations: 
      name: "Paris Dauphine - PSL"
      city: Paris
      state: France
date : "last-modified"
toc: true
number-sections: true
number-depth: 5
format:
  html:
    theme:
      light: yeti
      dark: darkly
    code-fold: true
    code-summary: "Display code"
    code-tools: true #enables to display/hide all blocks of code
    code-copy: true #enables to copy code
    grid:
      body-width: 1000px
      margin-width: 100px
    toc: true
    toc-location: left
execute:
  echo: true
  warning: false
  message: false
editor: visual
fig-align: "center"
highlight-style: ayu
css: styles.css
reference-location: margin
---

## Libraries and loading data

```{r}
#| label: load-packages
#| message: false
library(reactable)
library(tidyverse)
library(networkD3)

list_articles <- read.csv2("nlp_full_data_final_18-08-2023.csv", encoding = "UTF-8") %>%
  rename("entry_number" = 1)
list_references <- read.csv2("nlp_references_final_18-08-2023.csv", encoding = "UTF-8") %>%
  rename("citing_art" = 1)
colnames(list_articles) <- gsub("\\.+", "_", colnames(list_articles)) # <1>
colnames(list_articles) <- gsub("^[[:punct:]]+|[[:punct:]]+$", "", colnames(list_articles)) # <2>
colnames(list_references) <- gsub("\\.+", "_", colnames(list_references))
colnames(list_references) <- gsub("^[[:punct:]]+|[[:punct:]]+$", "", colnames(list_references))

```

1.  We replace the dots by one single underscore in the column names. It's easier to manipulate.
2.  We delete the punctuation marks in the beginning and end of the column names.

## Co-authorship network of NLP marketing papers

Here, we manipulate our data to create a simple network using the [networkD3](http://christophergandrud.github.io/networkD3/) package. You can read the official CRAN [Documentation](https://cran.r-project.org/web/packages/networkD3/networkD3.pdf "NetworkD3 R documentation") here.

```{r}
#| label: authors-graph
#| column: page

authors <- list_articles %>%
  #filter(citedby_count > 10) %>%
  filter(subtypeDescription != "Erratum") %>%
  filter(marketing == 1) %>% # <1>
  select(entry_number, authname)

# get unique entry numbers
entry_numbers <- unique(authors$entry_number)

# create empty data frame with two columns "from" and "to"
pairs_df <- data.frame(from = character(), 
                       to = character())

# loop through each entry number and get all combinations of pairs of names two by two
for (i in 1:length(entry_numbers)) 
  {
    entry_num <- entry_numbers[i]
    names <- unique(authors$authname[authors$entry_number == entry_num])
    if (length(names) > 1) #we can't use combn(name, 2) for solo authors, hence the if condition
      {
        pairs <- combn(names, 2)
        pairs_df <- rbind(pairs_df, data.frame(from = pairs[1,], to = pairs[2,]))
      } 
    else #if there is only one author, we just add his name to both "from" and "to" columns: he appears in the graph as a solo node. 
      #It's sad but at least he's there
      {
        pairs_df <- rbind(pairs_df, data.frame(from = names, to = names))
      }
}

graph_collab_authors <- simpleNetwork(pairs_df,
        Source       = 1,           # column number of source
        Target       = 2,           # column number of target
        linkDistance = 50,          # distance between node. Increase this value to have more space between nodes
        charge       = -15,         # numeric value indicating either the strength of the node repulsion (negative value) or attraction (positive value)
        fontSize     = 14,          # size of the node names
        fontFamily   = "serif",     # font og node names
        linkColour   = "#666",       # colour of edges, MUST be a common colour for the whole graph
        nodeColour   = "#69b3a2",    # colour of nodes, MUST be a common colour for the whole graph
        opacity      = 0.9,         # opacity of nodes. 0=transparent. 1=no transparency
        zoom         = T            # Can you zoom on the figure?
        )

graph_collab_authors

# save the widget
htmlwidgets::saveWidget(graph_collab_authors,"graph_collab_authors.html")
readr::write_excel_csv2(pairs_df,"pairs_df.csv")
```

1.  We have an interest only in articles related to marketing because there are a lot of conferences or papers related to purely technical matters that have "consumer" in the source title.

The figure below is a network that shows co-authors connections. This is an undirected graph.

```{r}
#| label: data-manipulation-authors
#| column: page



authors_articles <- list_articles %>%
  filter(subtypeDescription != "Erratum") %>%
  filter(marketing == 1) %>%
  select(authname, prism_coverDate, dc_title, citedby_count) %>%
  arrange(authname)


reactable(authors_articles, striped = TRUE, filterable = TRUE, defaultPageSize = 5,
          columns = list(
          authname = colDef(name = "Name", minWidth = 40, align = "center"),
          prism_coverDate = colDef(name = "Date", minWidth = 40, align = "center"),
          dc_title = colDef(name = "Article Title", minWidth = 200, align = "center"),
          citedby_count = colDef(name = "Citations", minWidth = 30, align = "center"))
)

```

## Network of references

Here, we want to get an overview of important articles in the field of marketing using NLP methods. To do so, we construct the same network as before but analyzing references. The type of publication we consider here is noted on the right

Since the rendering with all the references (27710) would be to hard to render on this html page, we filter by the 500 most cited references.

```{r}
#| label: publication-type
#| column: margin
#| echo: false


#type of publications
dfsubtypedescription <- list_articles %>%
  filter(subtypeDescription != "Erratum") %>%
  distinct(subtypeDescription) %>%
  arrange(subtypeDescription) %>% 
  rename("Publication Type" = 1)

reactable(data = dfsubtypedescription, striped = FALSE)

```

```{r}
#| label: network-references
#| column: screen-left


references_df <- list_references %>%
  slice_max(citedby_count, n = 500) %>%
  select(citing_art, scopus_eid) %>%
  mutate(citing_art = str_sub(citing_art,11)) %>%
  mutate(scopus_eid = str_sub(scopus_eid,8))
  


references_graph <- simpleNetwork(references_df,
        Source       = 1,                 # column number of source
        Target       = 2,                 # column number of target
        linkDistance = 30,          # distance between node. Increase this value to have more space between nodes
        charge       = -100,                # numeric value indicating either the strength of the node repulsion (negative value) or attraction (positive value)
        fontSize     = 14,               # size of the node names
        fontFamily   = "serif",       # font og node names
        #linkColour  = "#666",        # colour of edges, MUST be a common colour for the whole graph
        #nodeColour  = "#black",     # colour of nodes, MUST be a common colour for the whole graph
        opacity      = 1,              # opacity of nodes. 0=transparent. 1=no transparency
        zoom         = T                   # Can you zoom on the figure?
        )
references_graph
# save the widget

#htmlwidgets::saveWidget(graph_collab_authors,"graph_collab_authors.html")
readr::write_excel_csv2(references_df,"references_df.csv")

```

```{r}
#| label: reactable-references
#| column: page

references_reactable <- list_references %>%
  distinct(scopus_eid)

references_reactable <- list_references %>%
  distinct(scopus_eid, .keep_all = TRUE) %>%
  select(scopus_eid, author_list_author_preferred_name_ce_indexed_name, prism_coverDate, title, sourcetitle, citedby_count) %>%
  mutate(scopus_eid = str_sub(scopus_eid,8))

reactable(
  references_reactable,
  striped = TRUE,
  filterable = TRUE,
  defaultPageSize = 5,
  columns = list(
    scopus_eid = colDef(name = "Ref ID", minWidth = 40, align = "center"),
    author_list_author_preferred_name_ce_indexed_name = colDef(name = "Author", minWidth = 60, align = "center"),
    prism_coverDate = colDef(name = "Date", minWidth = 40, align = "center"),
    title = colDef(name = "Title", minWidth = 100, align = "center"),
    sourcetitle = colDef(name = "Journal", minWidth = 70, align = "center"),
    citedby_count = colDef(name = "Citations", minWidth = 30, align = "center")
  )
)

```

```{r}

data_network_references <- list_references %>%
  mutate("auth" = ifelse(
    is.na(prism_coverDate) | prism_coverDate == "", 
    author_list_author_ce_indexed_name, 
    paste(author_list_author_ce_indexed_name, substr(prism_coverDate, 1, 4))
  )) %>%
  select(citing_art, scopus_eid, auth, prism_coverDate, sourcetitle, title) %>%
  mutate(citing_art = str_sub(citing_art,11)) %>%
  mutate(scopus_eid = str_sub(scopus_eid,8))

readr::write_excel_csv2(data_network_references,"data_network_references.csv")


```
